Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-19 paper/v1.0/sections/7_conclusions.tex
Correct conclusion

In summary, the primary purpose of this paper were to expand the current descriptions on trasport properties in dressed quantum Hall systems and our  detailed theoritical analysis shows that we were able to demostrate that recently introduced Floquet-Drude conductivty model can be adopted to extend the models that are used to describe the trasport characteristics in quantum Hall systems. Finally, we identify that our relizations of this paper can be used towards creating nanoscale quantum devices, understaning their mechanism and enhancing their performance. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as buiding blocks of next generation nanoscale electronic devices.

>>>>

In summary, the primary purpose of this paper were to expand the current descriptions on trasport properties in dressed quantum Hall systems and our  detailed theoritical analysis shows that we were able to demostrate that recently introduced Floquet-Drude conductivty model can be adopted to extend the models that are used to describe the trasport characteristics in quantum Hall systems. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum swtiching devices which are employed as the buiding blocks of next generation nano-electronic devices. Finally, we identified that our findings of this paper can be used towards understaning nanoscale quantum devices, enhancing their performance and inventing novel appliance.
